MSOA Industrial Electricty and Gas maps

### 2021-08-29 MSOA non domestic Elec and Gas.Rmd
using the maps for the mapping discussion section

```{r Mapping the electrcity consumption of the MSOAs Industrial Sector}
msoa_elecDatanondom$MSOA11CD <- msoa_elecDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_nondom <-merge(msoa_sf_data, msoa_elecDatanondom)
ggplot2::ggplot(msoa_merged_sf_nondom) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
####Map Overlay
```{r Check leaflet for non dom elec consumption}
library (leaflet)

>>>>

```{r Mapping the electrcity consumption of the MSOAs Industrial Sector}
msoa_elecDatanondom$MSOA11CD <- msoa_elecDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_nondom <-merge(msoa_sf_data, msoa_elecDatanondom)
ggplot2::ggplot(msoa_merged_sf_nondom) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
mean(msoa_merged_sf_nondom$`Mean consumption (kWh per meter)`)
```
####Map Overlay
```{r Check leaflet for non dom elec consumption}
library (leaflet)
